cardinalR: Generating interesting high-dimensional data structures

### 2025-04-21 paper-cardinalR.Rmd
Added plan for the application

@@

@@

# Example

Add one or two datasets and evaluate how it will be useful.... (one with NLDR, one with clustering)

>>>>

Add main function argument list to a table...

@@

Add table of odd shapes..

@@

# Application

1) Generate a data structure with different shapes (two non-linear, one gaussian, one linear, one cone in 5-D simplex) and fit different NLDR

2) Add background noise to the same data by linking two or three clusters, then discuss how single and complete linkage affect for the solutions
